Exoplanet population inference and the abundance \\ of Earth analogs from noisy, incomplete catalogs

### 2014-06-11 document/ms.tex
updating figshare urls

We generate synthetic catalogs from two qualitatively different rate density
functions.
Both distributions are generated by a separable model
\begin{eqnarray}
\rate_\ratepars (\ln\period,\,\ln\radius) &=&
    \rate_\ratepars^{(\period)}(\ln\period)\,
    \rate_\ratepars^{(\radius)}(\ln\radius)
\end{eqnarray}
but fit using the full general model.
The first catalog---\modela---is generated assuming a smooth occurrence
surface where both distributions are broken power laws.
The second---\modelb---is designed to be exactly the distribution inferred by
\citet{petigura} in the range that they considered and then smoothly
extrapolated outside that range.
The catalogs generated from these two models are shown in \fig{smooth-results}
and \fig{simulation-results}, respectively and the data are available
online\footnote{\url{%
http://figshare.com/articles/Exoplanet_population_inference/1051864}}.

@@

We directly applied our method to the \citet{petigura} sample and generated
MCMC samples from the posterior probability for the occurrence rate density
step heights, marginalizing over the hyperparameters of the Gaussian process
model.
The resulting MCMC chain is available online\footnote{\url{%
http://figshare.com/articles/Exoplanet_population_inference/1051864}}.

@@

Some of the caveats on the results in this paper are due to assumptions made
for computational simplicity but a much more robust study would be possible
given a complete representation of the posterior probability function for the
physical parameters in the catalog.
The use of MCMC to fit models to observations is becoming standard practice in
astronomy and the results in many catalogs (including \citealt{petigura}) are
given as statistics computed on posterior samplings.
For the sake of hierarchical inferences like the method presented here, it
would be very useful if the authors of upcoming catalogs also published
samples from these distributions \emph{along with the value of their prior
function evaluated at each sample}.
In this spirit, we have released the results of this paper as posterior
samplings\footnote{\url{%
http://figshare.com/articles/Exoplanet_population_inference/1051864}} for the
occurrence rate density function.

>>>>

We generate synthetic catalogs from two qualitatively different rate density
functions.
Both distributions are generated by a separable model
\begin{eqnarray}
\rate_\ratepars (\ln\period,\,\ln\radius) &=&
    \rate_\ratepars^{(\period)}(\ln\period)\,
    \rate_\ratepars^{(\radius)}(\ln\radius)
\end{eqnarray}
but fit using the full general model.
The first catalog---\modela---is generated assuming a smooth occurrence
surface where both distributions are broken power laws.
The second---\modelb---is designed to be exactly the distribution inferred by
\citet{petigura} in the range that they considered and then smoothly
extrapolated outside that range.
The catalogs generated from these two models are shown in \fig{smooth-results}
and \fig{simulation-results}, respectively and the data are available
online\footnote{\url{http://dx.doi.org/10.6084/m9.figshare.1051864}}.

@@

We directly applied our method to the \citet{petigura} sample and generated
MCMC samples from the posterior probability for the occurrence rate density
step heights, marginalizing over the hyperparameters of the Gaussian process
model.
The resulting MCMC chain is available online\footnote{\url{%
http://dx.doi.org/10.6084/m9.figshare.1051864}}.

@@

Some of the caveats on the results in this paper are due to assumptions made
for computational simplicity but a much more robust study would be possible
given a complete representation of the posterior probability function for the
physical parameters in the catalog.
The use of MCMC to fit models to observations is becoming standard practice in
astronomy and the results in many catalogs (including \citealt{petigura}) are
given as statistics computed on posterior samplings.
For the sake of hierarchical inferences like the method presented here, it
would be very useful if the authors of upcoming catalogs also published
samples from these distributions \emph{along with the value of their prior
function evaluated at each sample}.
In this spirit, we have released the results of this paper as posterior
samplings\footnote{\url{http://dx.doi.org/10.6084/m9.figshare.1051864}} for
the occurrence rate density function.
